Zero-Knowledge Credentials for Smart Contracts

### 2018-05-14 paper/paper.tex
Add text

\begin{abstract}
	Public blockchains present unique opportunities for the implementation of
	autonomous and trustless systems, but suffer from trade-offs between
	privacy and expressivity. In this paper we present an implementation of a
	zkSNARK-based
	anonymous credential scheme for the Ethereum blockchain and give
	benchmarks for usage costs. We present as well an example application.
\end{abstract}

\section{Introduction}
While blockchains have found use cases in publicly accessible distributed
systems, they pose a challenge in that due to their public nature it is
currently impossible to attest to aspects of one's identity without some
trusted credential issuer.

@@

\subsection{Implementation}
We implement zero-knowledge proofs using the elliptic curve pairing precompiled
contracts in Ethereum, using the Pinnochio protocol
\cite{parnoPinocchioNearlyPractical2013}. We constructed the arithmetic circuits
for the proofs using libsnark \cite{ben-sassonSNARKsVerifyingProgram2013}.
Commitment trees are stored using IPFS \cite{benetIPFSContentAddressed2014}.

\section{Properties and Features}
Our zero-knowledge identity system allows for highly flexible ad-hoc issuance of
credentials through \textit{k-show} credentials and range-bounded attributes.

The public inputs are
\begin{equation*}
  \texttt{m\_root},\ \{l_1, \dots, l_7\},\ \{u_1, \dots, u_7\}, S, k
\end{equation*}

Each proof is an assertion that the prover holds a credential
\begin{equation*}
c = (sk, \{attr_1, \dots, attr_7\})  
\end{equation*}
 such that

\begin{enumerate}[1.]
\item The credential is a leaf of a merkle tree with root \texttt{m\_root}.
\item The credential contains some attributes $\{attr_1, \dots, attr_7\}$ with
  $attr_i \in [l_i,u_i]$
\item The credential has been used fewer than $k$ times with the salt $S$
\end{enumerate}

@@

\subsection{Credentials}
Each credential is of the form
\begin{equation*}
c =  ( \texttt{sk}, \{attr_1, \dots, attr_n\})
\end{equation*}

@@

\subsection{Credential Requests}
A credential request is a tuple of the form
\begin{equation*}
  r = (\texttt{merkle\_root}, \texttt{serial}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k)
\end{equation*}

where $\texttt{merkle\_root}$ is the root of a Merkle-tree of valid credential
commitments, $u_i, \ell_i \in \Z_{2^{32}}$ are bounds on acceptable attribute
values, $S$ is a request-specific salt, and $k\in \N$ is the allowed number of
uses of a single credential per salt $S$.

\subsection{k-show Credentials}
Every proof $\pi$ that a user generates has as public input
$\texttt{serial}_\pi$ which is defined as
\begin{equation*}
  H(\texttt{sk}_u || S_v || k)
\end{equation*}

@@

\subsection{Bounded-attributes}
A proof for a given credential request $r$ must assert that $attr_i \in [\ell_i,
u_i]$ for all $1\leq i\leq n$. This allows attestations such as ``I possess over
\$1 million'', ``I am between the ages of 21 and 45'', or ``I live in the USA'',
without revealing any additional information.

\subsection{Credential Scheme}
verifier

>>>>

\begin{abstract}
	Public blockchains present unique opportunities for the implementation of
	autonomous and trustless systems, but suffer from trade-offs between
	privacy and expressivity. In this paper we present an implementation of a
	zkSNARK-based
	anonymous credential scheme for the Ethereum blockchain and give
	benchmarks for usage costs. We present as an example application an
  age-verification contract.
\end{abstract}

\section{Introduction}
While blockchains have found use cases in publicly accessible distributed
systems, they pose a challenge in that due to their public nature it is
currently impossible to attest to aspects of one's identity without the
participation of a trusted credential issuer. Many distributed applications have
some responsibility to verify aspects of their users' identity, such as age or
place of residence, but would ideally not reveal anything else about the user,
including metadata about past and future attestations of identity.

@@

\subsection{Approach}
We implement zero-knowledge proofs using the elliptic curve pairing precompiled
contracts in Ethereum, using the Pinnochio protocol
\cite{parnoPinocchioNearlyPractical2013}. We constructed the arithmetic circuits
for the proofs using libsnark \cite{ben-sassonSNARKsVerifyingProgram2013}.
Commitment trees are stored using IPFS \cite{benetIPFSContentAddressed2014}.

@@

\subsection{Credentials}

\subsubsection{Credential Contents}
Each credential is of the form
\begin{equation*}
c =  ( \texttt{sk}, \{attr_1, \dots, attr_n\})
\end{equation*}

@@

\subsubsection{Credential Requests}
A credential request is a tuple of the form
\begin{equation*}
  r = (\texttt{merkle\_root}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k\_bound)
\end{equation*}

where $\texttt{merkle\_root}$ is the root of a Merkle-tree of valid credential
commitments, $u_i, \ell_i \in \Z_{2^{32}}$ are bounds on acceptable attribute
values, $S$ is a request-specific salt, and $k\_bound\in \N$ is the allowed number of
uses of a single credential per salt $S$.

\subsubsection{k-show Credentials}
Every proof $\pi$ that a user generates has as public input
$\texttt{serial}_\pi$ which is defined as
\begin{equation*}
  H(\texttt{sk}_u || S_v || k)
\end{equation*}

@@

\subsubsection{Bounded-attributes}
A proof for a given credential request $r$ must assert that $attr_i \in [\ell_i,
u_i]$ for all $1\leq i\leq n$. This allows attestations such as ``I possess over
\$1 million'', ``I am between the ages of 21 and 45'', or ``I live in the USA'',
without revealing any additional information.

\subsubsection{Arithmetic Circuit}
The verification algorithm for credentials is encoded as a rank-1 constraint
system, and accepts as public input a credential request $r$ along with a serial
number \texttt{serial}, and as private
input
\begin{equation*}
  aux = (c, k, M)
\end{equation*}
where $c$ is the credential satisfying request $r$, $k$ is the nonce that
generates $\texttt{serial}$, and $M$ is a merkle proof giving the authentication
path for $c$. The circuit constrains
\begin{itemize}
\item $M$ to be a valid merkle proof for $c$ in
  the tree with root $\texttt{merkle\_root}$
\item $k \leq k\_bound$
  \item  $\ell_i\leq
    attr_i\leq u_i$
  \item \texttt{serial} = $ H(\texttt{sk}_u || S_v || k)$
\end{itemize}

The verifier accepts if the proof satisfies this circuit and \texttt{serial} is
not in its nullifier set $N$.
